Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-01-11 paper/paper.tex
pass

\pgfplotsset{width=6cm,compat=1.8}
\pgfplotsset{every tick label/.append style={font=\tiny}}
\begin{figure}[t!]
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,2134) (1,9164) (2,5103) (3,5841) (4,1987) (5,1622) (6,805) (7, 535) (8, 340) (9,154) (10, 53)};
      \end{axis}
    \end{tikzpicture}
  }
  \caption{\label{fig:distribution-contents}Histogram of number of
    \CodeIn{content} options per rule.}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          ybar stacked,
          enlargelimits=0.09,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          %          ylabel={\#rules},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          xticklabel style={rotate=45},          
          nodes near coords,
          every node near coord/.append style={font=\scriptsize},        
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,11) (1,1301) (2,4910) (3,3662) (4,3250) (5,5353) (6,2911) (7, 1337) (8, 1246) (9,763) (10, 495)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-2ex}
  \caption{\label{fig:distribution-rule-size}Distribution of rule
    size.}
\end{figure}

@@

@@

Componente 2: Quantidade de contents na regra (histograma da figura 6)
Regras com uma quantidade mais comum de contents pontuam mais.
Assim como no caso anterior, a pontuação dada por esse componente será: \[\frac{rules\_per\_number\_of\_contents[len(rule)]}{max(rules\_per_number\_of\_contents)}\]

>>>>

@@

\pgfplotsset{width=6cm,compat=1.8}
\pgfplotsset{every tick label/.append style={font=\tiny}}

\begin{figure}[H]
  \centering
  \scalebox{1.2}{
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,11) (1,1301) (2,4910) (3,3662) (4,3250) (5,5353) (6,2911) (7, 1337) (8, 1246) (9,763) (10, 495)};
      \end{axis}
    \end{tikzpicture}
  }
  \vspace{-2ex}
  \caption{\label{fig:distribution-rule-size}Distribution of rule sizes.}
\end{figure}

@@

\subsubsection{Number of content options.} We empirically observed that content options are very
common. As consequence, we defined a heuristic function that takes the
number of content options into account. We calculate the contribution
of number of content options with the following formula:

\begin{figure}[t!]
  \centering
  \scalebox{1.2}{  
    \begin{tikzpicture}
      \begin{axis}[
          bar width=6pt,
          scaled ticks=false,
          tick label style={/pgf/number format/fixed},
          ybar stacked,
          enlargelimits=0.15,
          legend style={at={(0.5,-0.15)},
            anchor=north,legend columns=-1},
          symbolic x coords={0, 1, 2, 3, 4, 5, 6, 7, 8, 9, 10},
          xtick=data,
          nodes near coords,
          every node near coord/.append style={font=\tiny},
          nodes near coords align={vertical},
        ]
        \addplot coordinates {(0,2134) (1,9164) (2,5103) (3,5841) (4,1987) (5,1622) (6,805) (7, 535) (8, 340) (9,154) (10, 53)};
      \end{axis}
    \end{tikzpicture}
  }
  \caption{\label{fig:distribution-contents}Distribution of number of
    content options.}
\end{figure}

\[\frac{\mathit{rules\_per\_number\_of\_contents[len(rule)]}}{\mathit{max(rules\_per\_number\_of\_contents)}}\]

Note that the only difference compared to the formula to compute
contribution of size is the distribution used, which is given by the
term $\mathit{rules\_per\_number\_of\_contents}$ denoting a dictionary
of number of content options to number of rules that contain that
number of content options.

@@
